```{r}
library(tidyverse)

```

```{r}
df <- read_csv('https://covidtracking.com/data/download/all-states-history.csv') 
```

```{r}
names(df)
```
```{r}
library(lubridate)

df <- df%>%
  mutate(month = months(date),
       weekday = wday(date),
       monthday = mday(date))
```


```{r}
df <- df %>% 
mutate(daily_death = case_when(
  df$deathIncrease < 3 ~ 'low',
  df$deathIncrease >= 3 & df$deathIncrease <= 14 ~ 'medium',
  TRUE ~'high'))
```

```{r}
#df <- data.frame(day = c(1:31))

df$month2 <- case_when(
  df$monthday <= 10 ~ "early_month",
  df$monthday > 10 & df$monthday <= 20 ~ "mid_month",
  df$monthday > 20 ~ "end_month"
)
print(df)
```

```{r}
df <- df %>%
  mutate(weekend = ifelse(wday(date) %in% c(6, 7), 1, 0))
```

```{r}
df %>% select(-totalTestsViral)
```
```{r}
x <- c(1:10)
result <- x %>%
  sqrt() %>%
  sum() %>%
  
sum(x) 
### pipe
x %>% sum
```
```{r}
# square root of x
sqrt(x)
```
```{r}
x %>% sqrt
```
```{r}
sqrt(sum(x))
```
```{r}
x %>% sum %>% sqrt

```
```{r}
#
sum(sqrt(x))

```
```{r}
x %>% sqrt %>% sum
```
```{r}
log(sum(sqrt(x)))

```
```{r}
log(sum(x))

```
```{r}
# log base 2 of 16
log(16, 2)
```

-7.)This combo is used when you want to apply a function/calculation to different groups of the data. For example, to calculate the aver age number of cases (positiveIncrease) by dataQualityGrade, we use:
```{r}
df %>% 
  group_by(weekday) %>% ##change date to weekday at some point
  summarise(mean(positiveIncrease))
```
-Calculate the median number of cases (positiveIncrease) by month
```{r}
df %>% 
  group_by(month2) %>%
  summarise(median(positiveIncrease))
```
-Calculate the average number of cases (positiveIncrease) by month2
```{r}
df%>%
  group_by(month2) %>%
  summarise(mean(positiveIncrease))
```
-Calculate the median number of cases (positiveIncrease) by weekend
```{r}
df %>%
  group_by(weekend) %>%
  summarise(median(positiveIncrease))
```
8. Combo 2: filter + group_by + summarise
-An example: to calculate the average number of cases (positiveIncrease) in January and February separately, we use:
```{r}
df %>% 
  filter(month == 'January'| month == 'February') %>% 
  summarise(positve_increase = mean(positiveIncrease))
```
-Calculate the median number of cases (positiveIncrease) on the weekend by month in October and November 2020.
```{r}
df %>% 
  filter(month == 'October'|month== 'November') %>% 
  group_by(2020) %>% 
  summarise(positve_increase = median(positiveIncrease))
```
-Calculate the average number of death at different periods of a month (month2 variable) in Fall 2020
```{r}
df %>% 
  filter(month == 'October'| month == 'November' | month == 'December') %>% 
  group_by(2020) %>% 
  summarise(number_of_deaths = mean(death))
```
-Compare the average number of hospitalizations between weekdays and weekends in Summer 2020

9. Combo 3: filter + group_by + summarise + arrange
-Use the arrange function to find a month that has the highest number of deaths on the weekend.
```{r}
df %>% 
  filter(month == 'October'| month == 'November' | month == 'December') %>% 
  group_by(weekend) %>% 
    group_by(weekday) %>% 
        group_by(month) %>% 
  summarise(number_of_deaths = mean(death)) %>% 
arrange(-number_of_deaths)
```



```{r}
library(tidyverse)
df2=read_csv ("titanic.csv")
```


```{r}
df2 %>% select(Survived)
```
```{r}
df2 %>% filter(Survived==0)
```


```{r}
df2 %>% mutate(Passengerld = Survived - Age)
```



```{r}
df2 %>% arrange(Survived)

```

```{r}
df2 %>% summarise(Survived = mean(Survived, na.rm=TRUE))


```

```{r}
df2 %>% summarise(mean_death = mean(Survived, na.rm=TRUE), 
                 median_cases=median(Age, na.rm=TRUE), 
                 max_death=max(Survived, na.rm=TRUE))
## # A tibble: 1 x 3
```
```{r}
df2 %>% count(Sex)
```
```{r}
df2 %>% 
  group_by(Sex) %>% 
  summarise(Survived = mean(Survived))
```


```{r}
df2 %>% 
  count(Pclass) %>% 
  arrange(-n)
```


```{r}
df2 %>% 
  filter(Survived==0) %>% 
  group_by(Sex) %>% 
  summarise(survived = mean(Survived))
  
```

```{r}
df2 %>% 
  filter(Survived==0) %>% 
  group_by(Sex) %>% 
  summarise(survived = mean(Survived)) %>% 
  arrange(-survived)

```

```{r}

df2 %>% 
  filter(Sex =='female') %>% 
  count(Pclass) %>% 
  arrange(-n)
```

