---
title: "assignment4Extra"
author: "Kylia Medeiros"
date: "2024-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.) List all the names of the columns of the data
```{r}
library(tidyverse)
df <- read_csv('imdb_top_1000.csv')
```
2.) Which movies have the highest money earned (Gross)?

```{r}
df %>% 
  arrange(-Gross)
```
3.)What is the lowest rating (IMDB_Rating)? List five movies have this lowest rating.

```{r}
df %>% 
  arrange(IMDB_Rating)
```
4.)Which year have the most number of movies released in the list? What is the total of money earned on that year?
```{r}
df %>% 
  filter(Released_Year == 2014 ) %>% 
  group_by(Gross) %>%
  summary(df)
```

5.) What is the total money earned per movies on average?
```{r}
df %>% 
  summarise(mean_gross = mean(Gross, na.rm=TRUE))
```

6.) Calculate the average number of votes by year. Calculate the average number of votes of movies that have IMDB rating greater than 9.

```{r}
df %>% 
  group_by(Released_Year) %>% 
  summarise(votes = mean(No_of_Votes, na.rm = TRUE))
```

7.)Calculate the average Meta score in 2020 of movies that have number of votes in the third quartile.
```{r}
df %>% 
  filter(Released_Year == 2020 ) %>% 
  group_by('Meta_Score') %>%
  summary(df)
```
```{r}
# Select only character columns
df %>% select_if(is.character)

# Calculate the median of all numeric columns
df %>% summarise_if(is.numeric, mean, na.rm=TRUE)
```

9.)We can use select_if to select columns satisfying a condition and use summarise_if to do calculation on columns satisfying a condition. Try the follows to understand these functions.
```{r}
# Select only character columns
df %>% select_if(is.character)

# Calculate the median of all numeric columns
df %>% summarise_if(is.numeric, mean, na.rm=TRUE)
```
-arrange
```{r}
df %>% arrange(Genre)

```

-count
```{r}
df %>% count(Director)
```
-select
```{r}
df %>% select(Series_Title)

```
-mutate
```{r}
df %>% mutate(Runtime = IMDB_Rating - No_of_Votes)

```

-filter
```{r}
df %>% filter(Released_Year==2018)

```
-summarise
```{r}
df %>% summarise(IMDB_Rating = mean(IMDB_Rating, na.rm=TRUE))

```
-group_by and summarise
```{r}
df %>% 
  group_by(Genre) %>% 
  summarise(IMDB_Rating = mean(IMDB_Rating))
```
-count and arange
```{r}
df %>% 
  count(Genre) %>% 
  arrange(-n)
```
-Filter, group_by, and summarise
```{r}
df %>% 
  filter(Released_Year==2018) %>% 
  group_by(Genre) %>% 
  summarise(IMDB_Rating = mean(IMDB_Rating))
```

-Filter, count, and arrange
```{r}
df %>% 
  filter(Released_Year==2019) %>% 
  count(Genre) %>% 
  arrange(-n)
```



```