---
title: "assignment 5-part 1"
author: "Kylia Medeiros"
date: "2024-10-08"
output: html_document
---
-1.)Use read_csv to import the data. Show the number of NAs for each columns.

```{r}
library(tidyverse)
df <- read_csv('https://bryantstats.github.io/math421/data/adult_census_missing.csv')
na_count <- colSums(is.na(df))
print(na_count)
```
2.)Using function aggr the VIM package to plot the number of NAs for each column.
```{r}
library(VIM)
aggr(df, col = c("blue", "green"), number = TRUE, sortVars = TRUE)
```
-3.)Find other forms of missing values. Hint: You can use the table function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data.
```{r}
colSums(df == 'Missing', na.rm = TRUE)
```
-4.)Replace all the forms of missing values found to NA

```{r}
df <- replace(df, df == 'Unknown' |
                  df == 'Missing' |
                  df == 'Not Available', NA)
```

-5.)Replot the number of NAs for each column.
```{r}
aggr(df, col = c( "red", "yellow"), numbers = TRUE, sortVars = TRUE)
```
6.)Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs). How many rows left after removing?
```{r}
df2 = drop_na(df)
```

7.)Approach 2 to handle NAs: Fill all the NAs with the previous or next value. (Hint: Using fill function). Save the dataset after filling as a different data. The original data is unchanged (still have NAs)
```{r}
df3 = df %>% fill(age, sex, .direction = 'updown')
```

8.)Approach 3 to handle NAs: For numeric variable, replace the NAs by the median. For categorical variables, replace the NAs to the majority.
```{r}
median_age <- median(df$age, na.rm=TRUE)
df$age <- replace_na(df$age, median_age)

```

```{r}
df5 = majority_sex <- names(which.max(table(df$sex)))
df$sex <- replace_na(df$sex, majority_sex)


