---
title: "Assignment9"
author: "Kylia Medeiros"
date: "2024-11-05"
output: html_document
---
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
df <- read_csv('WHO-COVID-19-global-data.csv')
```

Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19.
```{r}
df %>% 
  filter(Date_reported == max(Date_reported))
```
```{r}
df %>% 
  arrange(-Cumulative_deaths)
```

2.)Use transition_reveal to make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
df %>%  
  ggplot(aes(x=Cumulative_deaths,
             y=Date_reported))+
  geom_line()+
  transition_reveal(Date_reported)
```


3.)Create the new variable (column) death_per_cases recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases). What are the three countries with the highest deaths per cases?
```{r}
df %>% 
  mutate(death_per_cases = Cumulative_deaths / Cumulative_cases) %>%   arrange(desc(death_per_cases)) %>% 
  head(3)
```



4.)Use transition_reveal to make a plot revealing the number of deaths per cases of the US, Italy and Mexico.
```{r}
df %>% 
  filter(Country %in% c('United States of America', 'Italy', 'Mexico')) %>% 
  ggplot(aes(y = Cumulative_deaths / Cumulative_cases,
             x = Date_reported,
             color = Country))+
  geom_line()+
  geom_point(size=3)+
  labs(y = 'Deaths Per Cases',
       x = 'Date')+
  transition_reveal(Date_reported)

```

5.)Import the following data https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv
```{r}
df1 <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv')
```

Use transition_reveal to plot the total vaccinations per hundred by level of income. Hint: the levels of income are identified in the location variable. Put a short comment on the caption of the plot.
```{r}
df1 %>% 
  filter(location %in% c('Upper middle income', 'Lower middle income', 'Low income', 'High income')) %>% 
  ggplot(aes(y = total_vaccinations_per_hundred,
             x = date ,
             color = location))+
  geom_line()+
  geom_point(size=3)+
  transition_reveal(date)
```

