---
title: "assignment7"
author: "Kylia Medeiros"
date: "2024-10-26"
output: html_document
---
```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
df <- read_csv('ds_salaries.csv')
```

```{r}
names(df)
```
```{r}
df
```
-Make a plot using facet_wrap by one categorical variable (facet_wrap(~variable1))
```{r}
ggplot(df, aes(x = work_year, y = salary)) +
  geom_point() +
  facet_wrap(~ experience_level)
```


Comment: (graph above)
This graph is showing the relationship between work year compared to an employees salary. There seems to be a higher salary for those working in 2021, and a lower salary for those in 2022. There is one outliter present in MI.

```{r}
ggplot(df, aes(x = work_year, y = salary)) +
  geom_point() +
  facet_wrap(~ experience_level + employment_type)

```
comment: (graph above)This graph shows how salary varies with work years, split by experience level and employment type. Overall giving insights into the relationship between experience and salary across different categories.

-Make a plot using position ='dodge'.
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x = work_year , fill = remote_ratio),
           position = 'dodge')
```

comment:(graph above)This graph shows the distribution of years worked and how it varies with different remote ratios. This graph is skewed left.

-Make a plot using position ='fill'.
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x = work_year , fill = remote_ratio), 
           position = 'fill')
```
comment:(graph above) This graph shows how remote work preference vary by work year. Each bar shows the different types of remote work, for different years worked.


This graph shows how work year, and remote ratio vary

-Make a plot using geom_col.
```{r}
df %>% 
  ggplot()+ 
  geom_col(mapping=aes(x = experience_level, y = salary))

```
comment: This graph shows the relationship between experience level and salary. Each bar on the x-axis represents the different expeirnece levels while the y represents salary. There is no skew in this graph, but alot of variation.

-Change the theme of one of your plots.
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x = work_year , fill = remote_ratio))+
theme_dark()
```
commment:The graph displays how remote work preferences vary by work year with the dark theme.This graph is skewed left.


Make a plot using combo filter + ggplot

```{r}
df %>%
  filter(work_year == 2020, remote_ratio == 0)
```
```{r}
  ggplot(df, aes(x = work_year, y = remote_ratio)) +
  geom_col()
```
comment: This graph seems to be skewed left, as the work years go on the remote ratios increase.

-Make a plot using combo group_by + summarise + geom_col
```{r}
df %>% 
  group_by(experience_level) %>%
  summarise(averageSalary = mean(salary, na.rm=TRUE)) %>% 
  ggplot()+ 
  geom_col(mapping=aes(x = experience_level, y = averageSalary))
```
-comment: This graph has alot of different variation and a slight skew left, this shows the relationship between average salary and the correlation to experience level.


```{r}
gg <- df %>% 
  group_by(experience_level) %>%
  summarise(averageSalary = mean(salary, na.rm=TRUE)) %>% 
  ggplot()+ 
  geom_col(mapping=aes(x = experience_level, y = averageSalary))
```


