---
title: "Midterm Project-R"
author: "Kylia Medeiros"
date: "2024-11-19"
output: html_document
---

```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(haven)
library(dplyr)
```


```{r, eval=FALSE}
df = read_sas('hdd0318cy.sas7bdat')
```


```{r}
names(df)
```

3.) Filter the data to have only patients of the year 2018 (yod=18)
```{r, eval=FALSE}
df = df %>% 
  filter(yod==18)
```

4.)Select to work with only following variables:
```{r, eval=FALSE}
library(dplyr)
df = df[, c("yod", "payfix","pay_ub92","age",  
                      "sex","raceethn","provider","moa", 
                      "yoa","mod","admtype", "asource" , 
                      "preopday" ,"los", "service" , "icu","ccu",    
                      "dispub92", "payer"  ,"drg","trandb", 
                      "randbg","randbs","orr", "anes","seq",   
                      "lab","dtest", "ther","blood","phar", 
                      "other","patcon","bwght","total","tot" ,  
                      "ecodub92","b_wt","pt_state","diag_adm","ancilar" ,
                      "campus","er_fee","er_chrg","er_mode","obs_chrg",
                      "obs_hour","psycchrg","nicu_day",'race')]
```

Notice: You may want to save the current data to your computer for easy access later. To save the data file use write_csv(df, 'midterm.csv'), for example.
```{r, eval=FALSE}
write_csv(df, 'midterm.csv')
```


```{r, eval=FALSE}
df <- df %>%
  mutate(sex = case_when(
    sex == 1 ~ "Male",
    sex == 2 ~ "Female"
  ))
```


```{r, eval=FALSE}
df <- df %>% 
  mutate(provider = as.numeric(provider),
         provider = case_when(
    provider == 7201 ~ 'Newport',
    provider == 7202 ~ 'St. Joseph Health Services of RI',
    provider == 7203 ~ 'Memorial',
    provider == 7204 ~ 'Miriam',
    provider == 7205 ~ 'Rhode Island Hospital',
    provider == 7206 ~ 'Roger Williams',
    provider == 7209 ~ 'South County',
    provider == 7210 ~ 'Kent County',
    provider == 7211 ~ 'Westerly',
    provider == 7212 ~ 'Rehab of RI',
    provider == 7213 ~ 'Landmark Medical Center',
    provider == 7214 ~ 'Women and Infants',
    provider == 7215 ~ 'Bradley',
    provider == 7216 ~ 'Butler',
  ))
```

```{r, eval=FALSE}
df$total <- as.numeric(df$total)
df$icu <- as.numeric(df$icu)

df <- df %>% 
  mutate(race = as.numeric(race),
         race = case_when(
           race == 1 ~ 'White',
           race == 2 ~ 'Black',
           race == 3 ~ 'Asian',
           race == 4 ~ 'American Indian',
           race == 5 ~ 'Hispanic',
           race == 6 ~ 'Other',
           race == 9 ~ 'Unknown',
           
         ))
```

```{r, eval=FALSE}
df <- df %>% 
  mutate(admtype = as.numeric(admtype),
         admtype = case_when(
           admtype == 1 ~ 'Emergency',
           admtype == 2 ~ 'Urgent',
           admtype == 3 ~ 'Electric',
           admtype == 4 ~ 'Newborn',
           admtype == 5 ~ 'Court Committal',
           admtype == 9 ~ 'Information Not Availble',
         
           ))
```

5.)What are variables that have missing values?

```{r, eval=FALSE}
na_count <- colSums(is.na(df))
print(na_count)
```
6.) 

```{r, eval=FALSE}
df1 = df


df2 = drop_na(df1)
```

7.) Refer to the data description in the file HDD2015-18cy6-20-19.docx, which variable recording the month of admission?, which variable recording the month of discharge?
```{r}
#Month of Admission = moa
#Month of Discharge = mod
```

8.) Which month admitted the most number of patients? Which month admitted the most number of male patients?
```{r}
df %>%
  group_by(moa) %>%
  count() %>%
  arrange(desc(n))
```


```{r}
df %>%
  filter(sex == 'Male') %>%
  group_by(moa) %>%
  count(moa) %>%
  arrange(-n)
```

9.) Which month has the most number of teenage female patients?
```{r}
df %>%
  filter(sex == "Female", age >= 13, age <=19 ) %>%
  group_by(moa) %>%
  count(moa) %>%
  arrange(-n)
```
10.) Which provider has the most number of female patients in October?
```{r}
df %>%
  group_by(provider) %>%
  filter(sex == 'Female', moa == '10')%>%
  count(provider) %>% 
  arrange(-n)
```

11.) Are female patients older than male patients, on average?
```{r}
df1 %>% 
  filter(sex == 'Female') %>% 
  summarise(female_age = mean(age))
```


```{r}
df1 %>% 
  filter(sex == 'Male') %>% 
  summarise(male_age = mean(age))
```
12.) Calculate the average age of patients by months. Which month has the oldest patients on average age?
```{r}
df1 %>% 
  group_by(moa) %>%
  summarise(average_age = mean(age)) %>% 
  arrange(-average_age)
```

13.) What is the name of the provider that has the highest total charge?
```{r}
df1 %>% 
  group_by(provider) %>% 
  summarise(total_charge = max(total)) %>% 
  arrange(desc(total_charge)) %>% 
  head(1)
```
14.) What is the name of the provider that has the least total charge for teenage male on average?
```{r}
df1 %>% 
  group_by(provider) %>%
  filter(sex == 'Male', age >= 13, age <=19 ) %>% 
  summarise(least_total = min(total)) %>% 
  count(provider) %>% 
  arrange(-n)
```
15.) Create a season (Spring, Summer, Fall, Winter) variable. Calculate the length of stays by season. Which season has the longest length of stays on average?
```{r}
df1 <- df1 %>%
  mutate(season = case_when(
    month(moa) %in% c(12, 1, 2) ~ "Winter",
    month(moa) %in% c(3, 4, 5) ~ "Spring",
    month(moa) %in% c(6, 7, 8) ~ "Summer",
    month(moa) %in% c(9, 10, 11) ~ "Fall"
  ))

season_average <- df1 %>%
  group_by(season) %>%
  summarise(length_of_stay = mean(los)) %>% 
  arrange(desc(length_of_stay))
season_average %>%
  filter(length_of_stay == max(length_of_stay))
```
16.) On average, how much a 20 year-old male get charged for staying 1 day in the Fall season?
```{r}
df1 %>% 
  group_by(sex == 'Male') %>% 
  filter(age == 21, season == 'Fall', los == 1) %>% 
  summarise(total = mean(total))
```


17.) Write a paragraph to summarize the section and give your comments on the results. You could do some other calculations to support your points.

-Regarding the admission trends, the highest number of admissions occurred in specific months with male and female patterns differing. For example, October saw the most female patients in certain age groups potentially reflecting seasonal healthcare trends. To ensure the quality of the analysis the missing values were identified and removed from the dataset. Patient age also varied across months, some having a higher proportion of older patients. This could be attributed to seasonal ingles or other healthcare trends. Notably, healthcare providers such as Rhode Island hospital reported the highest total charges, likely due to higher patient volume and broader range of services compared to other providers. The fall season had the longest average length of stay (LOS), which may be linked to the typical cold and flu season.

Comments: With Fall experiencing the highest patient volumes, healthcare providers can use this insight to better prepare for busy seasons. Understanding these patterns can help providers allocate resources more effectively, plan ahead for staffing and supplies, and ensure they are equipped to meet the increased demand during peak times.





II. Data Visualization
Continue with the data from part I.

Provides at least 10 meaningful plots. Comments on the plots. All plots should have title, caption, appropriate labels on x and y-axis

```{r}
df1 %>% 
  ggplot() +
  geom_bar(mapping=aes(x = sex, fill = season),
  position = 'dodge')+
  labs(title = "Seasonal Admissions", x = "Sex", y = "Number of Admissions")
```
```{r}
df1 %>% 
  ggplot() +
  geom_bar(mapping=aes(x = race, fill = sex),
  position = 'fill')+
  labs(title = "Seasonal Admissions: Based on Race", x = "Season", y = "Number of Admissions")
```
```{r}
ggplot(df1, aes(x = provider)) +
  geom_bar(fill = "blue", color = "red") +
  labs(title = "Provider Frequency", x = "Provider", y = "Frequency")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r}
df1 %>%
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 5) +
  labs(title = "Age Distribution by Race", x = "Age", y = "Count") +
  facet_wrap(~race)
```
```{r}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = los, color = sex)) +
  labs(title = "Age vs. Length of Stay", x = "Age", y = "Length of Stay (Days)")
```
```{r}
df1 %>% 
ggplot(aes(x = season, y = los)) +
  geom_boxplot(fill = "blue") +
  labs(title = "Length of Stay by Season", x = "Season", y = "Length of Stay (Days)")
```

```{r}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = icu, color = sex)) +
  labs(title = "Age vs. ICU Days", x = "Age", y = "ICU (Days)")
```
```{r}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = total, color = sex)) +
  labs(title = "Age vs. Total Charges", x = "Age", y = "Total Charges")
```

```{r}
df1 %>% 
  ggplot()+
  geom_smooth(aes(x = los, y = total))+
   labs(title = "Length of Stay vs. Total Charges", x = "Length of Stay", y = "Total Charges")
```
```{r}
df1 %>% 
  ggplot() +
  geom_bar(mapping=aes(x = admtype, fill = sex),
  position = 'dodge')+
  labs(title = "Admission Type per Sex", x = "Admission Type", y = "Number of Admissions")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
2.) Make an animation plot.
```{r}
library(gganimate)
g <- ggplot(df1, 
       aes(x = race, 
           y = los, 
           fill = sex))+
  geom_col() + 
  transition_states(season)+
labs(title = 'Season: {closest_state}')
animate(g)
```


3.)Write a paragraph to summarize the section and give your comments on the results.
-The analysis reveals the female patients had the higher admission across all seasons, especially in Spring and Summer, with Asian and American Indian women leading admissions rates. Rhode Island hospital handled the most cases likely due to broad services while smaller providers such as Bradley and Butler had fewer patients due to their specific personalized care.  
Admissions were influenced by age, with White individuals aged between 60-90 dominating and infants (age 0) being the notable outliers. The length of stay ranged between 50-100 days, but middle aged patients had more extended stays and charges were more influenced by stage duration than age. The ICU admissions were the highest for those aged 60-90 days evenly split between males and females. These trends can help provide better allocated resources and plan for peak demand periods.



III. Predictive Models
Continue with the data from part I. Make sure you do not have any missing values in the data. Use the follows as the target and input variables:

Target Variable: Create the target variable taking value of

low if the total charge of a patient (tot) is smaller than the median of the total charge, and

high otherwise.

Input Variables:

“age”,“sex”,“raceethn”,“provider”,“moa”,“mod”,“admtype”,“campus”, ‘los’

```{r}
#library(haven)
#df1 <-read_sas('hdd0318cy.sas7bdat')

total_charge <- median(df1$tot, na.rm = TRUE)

df1 <- df1 %>%
  mutate(target = case_when(
    tot < total_charge ~ "low",
    TRUE ~ "high"
  ))
df1 <- df1 %>% 
  select("age","sex","raceethn","provider","moa","mod","admtype","campus", 'los', 'target')
```

1.)Use filter function to filter out rows where raceethn=='' or admtype==''. Make sure all the categorical variables are factor, numeric variables are numeric. Set Training : Testing Split = 10 : 90
```{r}
df1 <- df1 %>%
  filter(!raceethn =='', !admtype =='')  
df1 <- df1 %>%
  mutate(
    target = as.factor(target),
    raceethn = as.factor(raceethn),
    provider = as.factor(provider),
    moa = as.factor(moa),
    mod = as.factor(mod),
    admtype = as.factor(admtype),
    campus = as.factor(campus),
    age = as.numeric(age),
    los = as.numeric(los)
  )
library(caret)

df1 <- drop_na(df1)

set.seed(2020)
splitIndex <- createDataPartition(df1$target, p = 0.10, list = FALSE)
df1_train <- df1[splitIndex, ]
df1_test <- df1[-splitIndex, ]
```

2.) Train a decision tree using rpart. Plot the decision tree. Plot the variable importance ranked by the tree.
```{r}
library(rpart) 
tree_model <- rpart(target ~ ., data = df1_train,
                 control = rpart.control(maxdepth = 3))
library(rattle)
fancyRpartPlot(tree_model)
```
```{r}
tree_model$variable.importance
```
```{r}
barplot(tree_model$variable.importance)
```
3.)Using caret for this question. Set Training Control to be: Use Cross-Validation of 5 folds across all models. Train & tune at least 2 different models (i.e. two different values for method= in the train function of caret). Plot the hyper-parameter tuning plots for each model.
```{r}
tuneGrid = expand.grid(maxdepth = 2:10)
trControl = trainControl(method = "cv",
                         number = 5)

tree_approach2 <- train(target~., data=df1_train, 
                                method = "rpart2", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)

plot(tree_approach2)
```
```{r}
library(caret)
pred <- predict(tree_approach2, df1_test)

cm <- confusionMatrix(data = pred, reference = df1_test$target)
cm$overall[1]
```
```{r}
library(randomForest)
forest_model = randomForest(target ~ ., data=df1_train, ntree = 5)

pred <- predict(forest_model, df1_test, type = "class")

cm <- confusionMatrix(data = pred, reference = df1_test$target, positive = "high")
cm$overall[1]
```
4.) Plot the comparison of the models in 3.
```{r}
trControl = trainControl(method = "cv",
                         number = 5)
tree <- train(target~., data=df1_train, 
                                method = "rpart2", 
                                trControl = trControl)
forest_ranger <- train(target~., data=df1_train, 
                    method = "ranger", 
                                trControl = trControl)

results <- resamples(list('Decision Tree' = tree,
                          'Random Forest' = forest_ranger))
bwplot(results)
```
This compares the performance metrics of the machine learning models: Random forest and the decision tree, it evaluates them using accuracy and kappa.

-We can see the random forest is outperforming the decision tree in both Kappa and accuracy


5.) What is your final selection for the model? Test the accuracy of your final model on the test data.
```{r}
pred <- predict(tree, df1_test)
cm <- confusionMatrix(data = pred, reference = df1_test$target, positive = "high")
cm$overall[1]
```

6.) Create another target variable (binary), decide the input variables and redo 1 to 5.

7.) Write a paragraph to summarize the section and give your comments on the results:
-Based on the information demonstrated by the plot, we can conclude that the random forest has the higher accuracy which suggests it outperforms the decision tree. Similarly the random forest also has a higher kappa value, meaning there is a better agreement compared to the decision tree. This indicates that the random forest is the best choice, for accuracy and kappa making it the more reliable machine learning model.
