---
title: "part 2"
author: "Kylia Medeiros"
date: "2024-12-06"
output: html_document
---
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(haven)
library(dplyr)
```



```{r, eval=FALSE}
df = read_sas('hdd0318cy.sas7bdat')
```

II. Data Visualization
Continue with the data from part I.

Provides at least 10 meaningful plots. Comments on the plots. All plots should have title, caption, appropriate labels on x and y-axis
```{r}
df1 = df
```

```{r}
df1 %>%
  ggplot(aes(x = sex, fill = moa)) +
  geom_bar(position = "dodge") +
  labs(title = "Seasonal Admissions", x = "Sex", y = "Number of Admissions")
```


```{r, eval=FALSE}
df1 %>% 
  ggplot() +
  geom_bar(mapping=aes(x = race, fill = sex),
  position = 'fill')+
  labs(title = "Seasonal Admissions: Based on Race", x = "Season", y = "Number of Admissions")
```


```{r, eval=FALSE}
ggplot(df1, aes(x = provider)) +
  geom_bar(fill = "blue", color = "red") +
  labs(title = "Provider Frequency", x = "Provider", y = "Frequency")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r, eval=FALSE}
df1 %>%
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 5) +
  labs(title = "Age Distribution by Race", x = "Age", y = "Count") +
  facet_wrap(~race)
```


```{r, eval=FALSE}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = los, color = sex)) +
  labs(title = "Age vs. Length of Stay", x = "Age", y = "Length of Stay (Days)")
```


```{r, eval=FALSE}
df1 %>% 
ggplot(aes(x = moa, y = los)) +
  geom_boxplot(fill = "blue") +
  labs(title = "Length of Stay by Season", x = "Season", y = "Length of Stay (Days)")
```

```{r, eval=FALSE}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = icu, color = sex)) +
  labs(title = "Age vs. ICU Days", x = "Age", y = "ICU (Days)")
```


```{r, eval=FALSE}
df1 %>% 
  ggplot() +
  geom_point(aes(x = age, y = total, color = sex)) +
  labs(title = "Age vs. Total Charges", x = "Age", y = "Total Charges")
```

```{r, eval=FALSE}
df1 %>% 
  ggplot()+
  geom_smooth(aes(x = los, y = total))+
   labs(title = "Length of Stay vs. Total Charges", x = "Length of Stay", y = "Total Charges")
```



```{r, eval=FALSE}
df1 %>% 
  ggplot() +
  geom_bar(mapping=aes(x = admtype, fill = sex),
  position = 'dodge')+
  labs(title = "Admission Type per Sex", x = "Admission Type", y = "Number of Admissions")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


2.) Make an animation plot.
```{r, eval=FALSE}
library(gganimate)
g <- ggplot(df1, 
       aes(x = race, 
           y = los, 
           fill = sex))+
  geom_col() + 
  transition_states(moa)+
labs(title = 'Season: {closest_state}')
animate(g)
```


3.)Write a paragraph to summarize the section and give your comments on the results.
-The analysis reveals the female patients had the higher admission across all seasons, especially in Spring and Summer, with Asian and American Indian women leading admissions rates. Rhode Island hospital handled the most cases likely due to broad services while smaller providers such as Bradley and Butler had fewer patients due to their specific personalized care.  
Admissions were influenced by age, with White individuals aged between 60-90 dominating and infants (age 0) being the notable outliers. The length of stay ranged between 50-100 days, but middle aged patients had more extended stays and charges were more influenced by stage duration than age. The ICU admissions were the highest for those aged 60-90 days evenly split between males and females. These trends can help provide better allocated resources and plan for peak demand periods.
