
---
title: "Retail Store Performance - Check Box"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv('Store_CA.csv')
df$StoreAge <- mdy(df$StoreAge)

```

{.sidebar}
=======================================================================

KPI’s are key performance indicators, this dataset is a collection for retail stores which offers insights into factors including store performance, customer engagement, and financial outcomes. This helps understand the relationship between operational performance, store characteristics, and sales performance.

- In this example, the data for Date is not fictional and not real data. 

```{r}
dateRangeInput(inputId = "StoreAge_range", 
               label = h2("Select Store Age Range"), 
               start = min(df$Date_reported), 
               end = max(df$StoreAge_reported),
               min = min(df$StoreAge_reported), 
               max = max(df$StoreAge_reported))
```

Main Tab 1
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p1 <- df %>% 
    ggplot(aes(x=CustomerFootfall, color=StoreAge))+
    geom_density()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% 
    ggplot(aes(x=CustomerFootfall, fill=StoreAge))+
    geom_bar()
  ggplotly(p2)
})
```
