
---
title: "Retail Store Performance - Combination of Inputs"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv('Store_CA.csv')

```

{.sidebar}
=======================================================================

KPI’s are key performance indicators, this dataset is a collection for retail stores which offers insights into factors including store performance, customer engagement, and financial outcomes. This helps understand the relationship between operational performance, store characteristics, and sales performance.


```{r}
sliderInput(inputId = "revenue_input",
            label = h2("Select Monthly Sales Revenue Range"),
            min = min(df$MonthlySalesRevenue, na.rm = TRUE),
            max = max(df$MonthlySalesRevenue, na.rm = TRUE),
            value = c(min(df$MonthlySalesRevenue, na.rm = TRUE), 
                      max(df$MonthlySalesRevenue, na.rm = TRUE)))

selectInput(inputId = "store_size", 
            label = h3("Select Store Category"),
            choices = c("Clothing", "Electronics", "Grocery"), 
            selected = "Clothing")

library(shiny)
checkboxGroupInput(inputId = "StoreLocation_input", 
                   label = h3("Store Location"),
                   choices = unique(df$StoreLocation), 
                   inline = TRUE,
                   selected = unique(df$StoreLocation)[1])


checkboxGroupInput(inputId = "PromotionsCount_input", 
                   label = h3("Promotions Count"),
                   choices = unique(df$PromotionsCount), 
                   inline = TRUE,
                   selected = unique(df$PromotionsCount)[1])

selectInput(inputId = "store_age", 
            label = h3("Select Store Age"),
            choices = c("1:15", "6:30", "31:50"), 
            selected = "1:15")

```

Main Tab 1
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p1 <- df %>% 
    ggplot(aes(x=CompetitorDistance, color=StoreAge))+
    geom_density()
  ggplotly(p1)
})
```


Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% 
    filter(MonthlySalesRevenue>input$revenue_input[1],MonthlySalesRevenue<input$revenue_input[2]) %>% 
    filter(StoreCategory==input$store_size) %>% 
    filter(StoreLocation %in% input$StoreLocation_input) %>% 
  ggplot(aes(x=PromotionsCount, fill=StoreSize))+
    geom_bar()
  ggplotly(p2)
})
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p1 <- df %>% 
        filter(MonthlySalesRevenue>input$revenue_input[1],MonthlySalesRevenue<input$revenue_input[2]) %>% 
    filter(StoreCategory==input$store_size) %>% 
    filter(StoreLocation %in% input$StoreLocation_input) %>% 
    ggplot(aes(x=StoreCategory, color=StoreLocation))+
    geom_density()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### What is Density Plot?

- A density plot is an alternative to Histogram used for visualizing the distribution of a continuous variable. The peaks of a Density Plot help to identify where values are concentrated over the interval of the continuous variable. Compared to Histograms, Density Plots are better at finding the distribution shape because they are re not affected by the number of bins used (each bar used in a typical histogram).

- For example, a Histogram with only 4 bins wouldn’t produce a distinguishable enough shape of distribution as a 30-bin Histogram would. However, with Density Plots, this isn’t an issue.




![](https://datavizcatalogue.com/methods/images/top_images/SVG/density_plot.svg)



Main Tab 3
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
df %>% 
  ggplot() +
  geom_bar(mapping=aes(x = StoreCategory, fill = StoreLocation),
  position = 'fill')+
  labs(title = "Marketing Spend: Based on Promotions Count", x = "StoreCategory", y = "PromotionsCount")
```

Column {data-width=500}
-----------------------------------------------------------------------

### What is Bar Chart?

- There are two types of bar charts: geom_bar() and geom_col(). geom_bar() makes the height of the bar proportional to the number of cases in each group (or if the weight aesthetic is supplied, the sum of the weights). 

- If you want the heights of the bars to represent values in the data, use geom_col() instead. geom_bar() uses stat_count() by default: it counts the number of cases at each x position. geom_col() uses stat_identity(): it leaves the data as is.

```{r}
image_url <- "https://centralca.cdn-anvilcms.net/media/images/2020/02/19/images/California-map_Living_1.max-2400x1350.png"
```
<center><img src="`r image_url`"></center>

Main Tab 4
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Search Bar
```{r}
datatable(df, options = list(
  pageLength = 25
))
```


Column {data-width=500}
-----------------------------------------------------------------------
