
---
title: "Retail Performance - Check Box"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
df <- read_csv('Store_CA.csv')
df$StoreAge = factor(df$StoreAge)
df$StoreLocation = factor(df$StoreLocation)

titanic_sex <- unique(df$Sex)
```

{.sidebar}
=======================================================================

KPI’s are key performance indicators, this dataset is a collection for retail stores which offers insights into factors including store performance, customer engagement, and financial outcomes. This helps understand the relationship between operational performance, store characteristics, and sales performance.

```{r}
sliderInput(inputId = "revenue_input",
            label = h2("Select Monthly Sales Revenue Range"),
            min = min(df$MonthlySalesRevenue, na.rm = TRUE),
            max = max(df$MonthlySalesRevenue, na.rm = TRUE),
            value = c(min(df$MonthlySalesRevenue, na.rm = TRUE), 
                      max(df$MonthlySalesRevenue, na.rm = TRUE)))

```

Main Tab 1
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p1 <- df %>% 
    ggplot(aes(x=MonthlySalesRevenue, color=StoreLocation))+
    geom_density()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% 
    ggplot(aes(x=MarketingSpend, fill=PromotionsCount))+
    geom_bar()
  ggplotly(p2)
})
```
